\documentclass{article}
\setcounter{secnumdepth}{0}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=20mm,
top=20mm,
}
\title{Articles of Association for a Charitable Company Limited by Guarantee and not having a share capital}
\author{Project Upskill}
\date{January 2022}

\begin{document}

\maketitle
\tableofcontents
\newpage
\begin{enumerate}[label=\arabic*]
    \section{Articles of Association of Project Upskill}
    \item The company's name is Project Upskill (and in this document it is called the `charity').
    
    \section{Interpretation}
    \item In the articles:
    
    `address' means a postal address or, for the purposes of electronic
    communication, a fax number, an e-mail or postal address or a
    telephone number for receiving text messages in each case registered
    with the charity;
    
    `the articles' means the charity's articles of association;
    
    `the charity' means the company intended to be regulated by
    the articles;
    
    `clear days' in relation to the period of a notice means a
    period excluding:
    \begin{itemize}
        \item the day when the notice is given or deemed to be given; and
        \item the day for which it is given or on which it is to take effect;
    \end{itemize}
    
    `the Commission' means the Charity Commission for England and Wales;
    
    `Companies Acts' means the Companies Acts (as defined in section 2 of
    the Companies Act 2006) insofar as they apply to the charity;
    
    `the directors' means the directors of the charity. The directors are
    charity trustees as defined by section 177 of the Charities Act 2011;
    
    `document' includes, unless otherwise specified, any document sent or
    supplied in electronic form;
    
    `electronic form' has the meaning given in section 1168 of the
    Companies Act 2006;
    
    `the memorandum' means the charity's memorandum of association;
    
    `officers' includes the directors and the secretary (if any);
    
    `the seal' means the common seal of the charity if it has one;
    
    `secretary' means any person appointed to perform the duties of the
    secretary of the charity;
    
    `the United Kingdom' means Great Britain and Northern Ireland; and
    
    words importing one gender shall include all genders, and the singular
    includes the plural and vice versa.
    
    Unless the context otherwise requires words or expressions contained
    in the articles have the same meaning as in the Companies Acts but
    excluding any statutory modification not in force when this constitution
    becomes binding on the charity.
    
    Apart from the exception mentioned in the previous paragraph a
    reference to an Act of Parliament includes any statutory modification or
    re-enactment of it for the time being in force.
    \section{Liability of Members}
    \item The liability of the members is limited to a sum not exceeding £10,
    being the amount that each member undertakes to contribute to the
    assets of the charity in the event of its being wound up while he, she
    or it is a member or within one year after he, she or it ceases to be a
    member, for:
    \begin{enumerate}[label=(\arabic*)]
        \item payment of the charity's debts and liabilities incurred before he,
        she or it ceases to be a member;
        \item payment of the costs, charges and expenses of winding up; and
        \item adjustment of the rights of the contributories among themselves.
    \end{enumerate} 
    
    \section{Objects}
    \item The charity's objects (`Objects') are specifically restricted to
    the following:
    
    \begin{itemize}
        \item the advancement of education for young adults, particularly in life skills and mental well-being, in any way deemed fit by the directors;
        \item advancing education and raising awareness in equality and diversity; and
        \item to provide the community any input from the directors as they see fit to enable to create curated educational knowledge with free and open access under a public licence and to spread it amongst the wider community.
    \end{itemize}
    
    [Nothing in the articles shall authorise an application of the property
    of the charity for purposes which are not charitable in accordance with
    section 7 of the Charities and Trustee Investment (Scotland) Act 2005
    and/or section 2 of the Charities Act (Northern Ireland) 2008.]
    
    \section{Powers}
    \item The charity has power to do anything which is calculated to further
    its Object(s) or is conducive or incidental to doing so. In particular, the
    charity has power:
    
    \begin{enumerate}[label=(\arabic*)]
        \item to raise funds. In doing so, the charity must not undertake any
        taxable permanent trading activity and must comply with any
        relevant statutory regulations;
        
        \item to buy, take on lease or in exchange, hire or otherwise acquire
        any property and to maintain and equip it for use;
        \item to sell, lease or otherwise dispose of all or any part of the
        property belonging to the charity. In exercising this power, the
        charity must comply as appropriate with sections 117 and 122
        of the Charities Act 2011.
        \item to borrow money and to charge the whole or any part of the
        property belonging to the charity as security for repayment of
        the money borrowed or as security for a grant or the discharge
        of an obligation. The charity must comply as appropriate with
        sections 124 - 126 of the Charities Act 2011 if it wishes to
        mortgage land;
        \item to co-operate with other charities, voluntary bodies and
        statutory authorities and to exchange information and advice
        with them;
        \item to establish or support any charitable trusts, associations or
        institutions formed for any of the charitable purposes included
        in the Objects;
        \item to acquire, merge with or to enter into any partnership or joint
        venture arrangement with any other charity;
        \item to set aside income as a reserve against future expenditure but
        only in accordance with a written policy about reserves;
        \item to employ and remunerate such staff as are necessary for
        carrying out the work of the charity. The charity may employ
        or remunerate a director only to the extent it is permitted to do
        so by article 7 and provided it complies with the conditions in
        that article;
        \item to:
        \begin{enumerate}[label=(\alph*)]
            \item deposit or invest funds;
            \item employ a professional fund-manager; and
            \item arrange for the investments or other property of the
            charity to be held in the name of a nominee;
            in the same manner and subject to the same conditions as the
            trustees of a trust are permitted to do by the Trustee Act 2000;
        \end{enumerate}
        \item to provide indemnity insurance for the directors in accordance
        with, and subject to the conditions in, section 189 of the
        Charities Act 2011;
        \item to pay out of the funds of the charity the costs of forming and
        registering the charity both as a company and as a charity.
    \end{enumerate}
    
    \section{Application of income and property}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The income and property of the charity shall be applied solely
        towards the promotion of the Objects.
        \item \begin{enumerate}[label=(\alph*)]
            \item A director is entitled to be reimbursed from the property
            of the charity or may pay out of such property reasonable
            expenses properly incurred by him or her when acting on
            behalf of the charity.
            \item A director may benefit from trustee indemnity insurance
            cover purchased at the charity's expense in accordance
            with, and subject to the conditions in, section 189 of the
            Charities Act 2011.
            \item A director may receive an indemnity from the charity in
            the circumstances specified in article 57.
            \item A director may not receive any other benefit or payment
            unless it is authorised by article 7
        \end{enumerate}
        \item Subject to article 7, none of the income or property of the
        charity may be paid or transferred directly or indirectly by way
        of dividend bonus or otherwise by way of profit to any member
        of the charity. This does not prevent a member who is not also a
        director receiving:
        \begin{enumerate}[label=(\alph*)]
            \item a benefit from the charity in the capacity of a beneficiary
            of the charity;
            \item reasonable and proper remuneration for any goods or
            services supplied to the charity
        \end{enumerate}
    \end{enumerate}
    
    \section{Benefits and payments to charity directors and connected persons}
    \item \begin{enumerate}[label=(\arabic*)]
        \subsection{General provisions}
        
        \item No director or connected person may:
        \begin{enumerate}[label=(\alph*)]
            \item buy any goods or services from the charity on terms
            preferential to those applicable to members of the public;
            \item sell goods, services, or any interest in land to the charity;
            \item be employed by, or receive any remuneration from,
            the charity;
            \item receive any other financial benefit from the charity;
        \end{enumerate}
        
        unless the payment is permitted by sub-clause (2) of this article,
        or authorised by the court or the prior written consent of the
        Charity Commission has been obtained.
        
        In this article a `financial benefit' means a benefit, direct or indirect,
        which is either money or has a monetary value.
        
        \subsection{Scope and powers permitting directors' or connected persons' benefits}
        \item \begin{enumerate}[label=(\alph*)]
            \item A director or connected person may receive a benefit from
            the charity in the capacity of a beneficiary of the charity
            provided that a majority of the directors do not benefit in
            this way.
            \item A director or connected person may enter into a contract
            for the supply of services, or of goods that are supplied in
            connection with the provision of services, to the charity
            where that is permitted in accordance with, and subject
            to the conditions in, sections 185 and 186 of the Charities
            Act 2011.
            \item Subject to sub-clause (3) of this article a director or
            connected person may provide the charity with goods
            that are not supplied in connection with services provided
            to the charity by the director or connected person.
            \item A director or connected person may receive interest on
            money lent to the charity at a reasonable and proper rate
            which must be not more than the Bank of England bank
            rate (also known as the base rate).
            \item A director or connected person may receive rent for
            premises let by the director or connected person to the
            charity. The amount of the rent and the other terms of
            the lease must be reasonable and proper. The director
            concerned must withdraw from any meeting at which
            such a proposal or the rent or other terms of the lease are
            under discussion.
            \item A director or connected person may take part in the
            normal trading and fundraising activities of the charity on
            the same terms as members of the public.
        \end{enumerate}
        
        \subsection{Payment for supply of goods only – controls}
        \item The charity and its directors may only rely upon the authority
        provided by sub-clause (2)(c) of this article if each of the
        following conditions is satisfied:
        
        \begin{enumerate}[label=(\alph*)]
            \item The amount or maximum amount of the payment for
            the goods is set out in an agreement in writing between
            the charity or its directors (as the case may be) and the
            director or connected person supplying the goods (`the
            supplier') under which the supplier is to supply the goods
            in question to or on behalf of the charity.
            \item The amount or maximum amount of the payment for
            the goods does not exceed what is reasonable in the
            circumstances for the supply of the goods in question.
            \item The other directors are satisfied that it is in the best
            interests of the charity to contract with the supplier rather
            than with someone who is not a director or connected
            person. In reaching that decision the directors must
            balance the advantage of contracting with a director or
            connected person against the disadvantages of doing so.
            \item The supplier is absent from the part of any meeting at
            which there is discussion of the proposal to enter into a
            contract or arrangement with him or her or it with regard
            to the supply of goods to the charity.
            \item The supplier does not vote on any such matter and is not
            to be counted when calculating whether a quorum of
            directors is present at the meeting.
            \item The reason for their decision is recorded by the directors
            in the minute book.
            \item A majority of the directors then in office are not in receipt
            of remuneration or payments authorised by article 7.
        \end{enumerate}
        \item In sub-clauses (2) and (3) of this article:
        \begin{enumerate}[label=(\alph*)]
            \item `charity' includes any company in which the charity:
            \begin{enumerate}[label=(\roman*)]
                \item  holds more than 50\\% of the shares; or
                \item controls more than 50\\% of the voting rights
                attached to the shares; or
                \item has the right to appoint one or more directors to the
                board of the company.
            \end{enumerate}
            \item `connected person' includes any person within the
            definition in article 61 `Interpretation'.
        \end{enumerate}
    \end{enumerate}
    
    \section{Declaration of directors' interests}
    \item A director must declare the nature and extent of any interest, direct or
    indirect, which he or she has in a proposed transaction or arrangement
    with the charity or in any transaction or arrangement entered into by
    the charity which has not previously been declared. A director must
    absent himself or herself from any discussions of the charity directors
    in which it is possible that a conflict will arise between his or her duty
    to act solely in the interests of the charity and any personal interest
    (including but not limited to any personal financial interest).
    
    \section{Conflicts of interests and conflicts of loyalties}
    \item \begin{enumerate}[label=(\arabic*)]
        \item If a conflict of interests arises for a director because of a duty of
        loyalty owed to another organisation or person and the conflict
        is not authorised by virtue of any other provision in the articles,
        the unconflicted directors may authorise such a conflict of
        interests where the following conditions apply:
        \begin{enumerate}[label=(\alph*)]
            \item the conflicted director is absent from the part of the
            meeting at which there is discussion of any arrangement
            or transaction affecting that other organisation or person;
            \item the conflicted director does not vote on any such matter
            and is not to be counted when considering whether a
            quorum of directors is present at the meeting; and
            \item the unconflicted directors consider it is in the interests
            of the charity to authorise the conflict of interests in the
            circumstances applying.
        \end{enumerate}
        \item In this article a conflict of interests arising because of a duty of
        loyalty owed to another organisation or person only refers to
        such a conflict which does not involve a direct or indirect benefit
        of any nature to a director or to a connected person
    \end{enumerate}
    
    \section{Members}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The subscribers to the memorandum are the first members of
        the charity.
        \item Membership is open to other individuals or organisations who:
        \begin{enumerate}[label=(\alph*)]
            \item apply to the charity in the form required by the
            directors; and
            \item are approved by the directors.
        \end{enumerate}
        \item \begin{enumerate}[label=(\alph*)]
            \item The directors may only refuse an application for
            membership if, acting reasonably and properly, they
            consider it to be in the best interests of the charity to
            refuse the application.
            \item The directors must inform the applicant in writing of
            the reasons for the refusal within twenty-one days of
            the decision.
            \item The directors must consider any written representations
            the applicant may make about the decision. The directors'
            decision following any written representations must be
            notified to the applicant in writing but shall be final.
        \end{enumerate}
        \item Membership is not transferable.
        \item The directors must keep a register of names and addresses of
        the members.
    \end{enumerate}
    
    \section{Classes of membership}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors may establish classes of membership with
        different rights and obligations and shall record the rights and
        obligations in the register of members.
        \item The directors may not directly or indirectly alter the rights or
        obligations attached to a class of membership.
        \item The rights attached to a class of membership may only be
        varied if:
        \begin{enumerate}[label=(\arabic*)]
            \item three-quarters of the members of that class consent in
            writing to the variation; or
            \item three-quarters of the members of that class consent in
            writing to the variation; or
        \end{enumerate}
        \item The provisions in the articles about general meetings shall apply
        to any meeting relating to the variation of the rights of any class
        of members.
    \end{enumerate}
    
    \section{Termination of membership}
    \item Membership is terminated if:
    \begin{enumerate}[label=(\arabic*)]
        \item the member dies or, if it is an organisation, ceases to exist;
        \item the member resigns by written notice to the charity unless, after
        the resignation, there would be less than two members;
        \item any sum due from the member to the charity is not paid in full
        within six months of it falling due;
        \item the member is removed from membership by a resolution of
        the directors that it is in the best interests of the charity that his
        or her or its membership is terminated. A resolution to remove a
        member from membership may only be passed if:
        \begin{enumerate}[label=(\alph*)]
            \item the member has been given at least twenty-one days'
            notice in writing of the meeting of the directors at which
            the resolution will be proposed and the reasons why it is
            to be proposed;
            \item the member or, at the option of the member, the
            member's representative (who need not be a member of
            the charity) has been allowed to make representations to
            the meeting.
        \end{enumerate}
    \end{enumerate}
    
    \section{General meetings}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The charity must hold its first annual general meeting within
        eighteen months after the date of its incorporation.
        \item An annual general meeting must be held in each subsequent
        year and not more than fifteen months may elapse between
        successive annual general meetings.
    \end{enumerate}
    \item The directors may call a general meeting at any time.
    
    \section{Notice of general meetings}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The minimum periods of notice required to hold a general
        meeting of the charity are:
        \begin{enumerate}[label=(\alph*)]
            \item twenty-one clear days for an annual general meeting
            or a general meeting called for the passing of a
            special resolution;
            \item fourteen clear days for all other general meetings.
        \end{enumerate}
        \item A general meeting may be called by shorter notice if it is so
        agreed by a majority in number of members having a right to
        attend and vote at the meeting, being a majority who together
        hold not less than 90 percent of the total voting rights.
        \item The notice must specify the date time and place of the meeting
        and the general nature of the business to be transacted. If the
        meeting is to be an annual general meeting, the notice must
        say so. The notice must also contain a statement setting out the
        right of members to appoint a proxy under section 324 of the
        Companies Act 2006 and article 22.
        \item  The notice must be given to all the members and to the
        directors and auditors.
    \end{enumerate}
    \item The proceedings at a meeting shall not be invalidated because a person
    who was entitled to receive notice of the meeting did not receive it
    because of an accidental omission by the charity.
    
    \section{Proceedings at general meetings}
    \item \begin{enumerate}[label=(\arabic*)]
        \item No business shall be transacted at any general meeting unless a
        quorum is present.
        \item A quorum is:
        \begin{enumerate}[label=(\alph*)]
            \item three (3) members present in person or by proxy and entitled to
            vote upon the business to be conducted at the meeting; or
            \item one tenth of the total membership at the time
        \end{enumerate}
        whichever is the greater.
        
        \item The authorised representative of a member organisation shall
        be counted in the quorum.
    \end{enumerate}
    \item \begin{enumerate}[label=(\arabic*)]
        \item If:
        \begin{enumerate}[label=(\alph*)]
            \item a quorum is not present within half an hour from the time
            appointed for the meeting; or
            \item during a meeting a quorum ceases to be present;
        \end{enumerate}
        the meeting shall be adjourned to such time and place as the
        directors shall determine.
        \item The directors must reconvene the meeting and must give at
        least seven clear days' notice of the reconvened meeting stating
        the date, time and place of the meeting.
        \item If no quorum is present at the reconvened meeting within
        fifteen minutes of the time specified for the start of the meeting
        the members present in person or by proxy at that time shall
        constitute the quorum for that meeting.
    \end{enumerate}
    \item \begin{enumerate}[label=(\arabic*)]
        \item General meetings shall be chaired by the person who has been
        appointed to chair meetings of the directors.
        \item If there is no such person or he or she is not present within
        fifteen minutes of the time appointed for the meeting a director
        nominated by the directors shall chair the meeting.
        \item If there is only one director present and willing to act, he or she
        shall chair the meeting.
        \item If no director is present and willing to chair the meeting within
        fifteen minutes after the time appointed for holding it, the
        members present in person or by proxy and entitled to vote
        must choose one of their number to chair the meeting.
    \end{enumerate}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The members present in person or by proxy at a meeting
        may resolve by ordinary resolution that the meeting shall
        be adjourned.
        \item The person who is chairing the meeting must decide the date,
        time and place at which the meeting is to be reconvened unless
        those details are specified in the resolution.
        \item No business shall be conducted at a reconvened meeting unless
        it could properly have been conducted at the meeting had the
        adjournment not taken place.
        \item If a meeting is adjourned by a resolution of the members for
        more than seven days, at least seven clear days' notice shall
        be given of the reconvened meeting stating the date, time and
        place of the meeting.
    \end{enumerate}
    \item \begin{enumerate}[label=(\arabic*)]
        \item Any vote at a meeting shall be decided by a show of hands
        unless before, or on the declaration of the result of, the show of
        hands a poll is demanded:
        \item \begin{enumerate}[label=(\alph*)]
            \item by the person chairing the meeting; or
            \item by at least two members present in person or by proxy
            and having the right to vote at the meeting; or
            \item by a member or members present in person or by proxy
            representing not less than one-tenth of the total voting
            rights of all the members having the right to vote at
            the meeting.
        \end{enumerate}
        \item \begin{enumerate}[label=(\alph*)]
            \item  The declaration by the person who is chairing the
            meeting of the result of a vote shall be conclusive unless
            a poll is demanded.
            \item If the demand for a poll is withdrawn the demand shall
            not invalidate the result of a show of hands declared
            before the demand was made.
        \end{enumerate}
        \item \begin{enumerate}[label=(\alph*)]
            \item A poll must be taken as the person who is chairing the
            meeting directs, who may appoint scrutineers (who need
            not be members) and who may fix a time and place for
            declaring the results of the poll.
            \item The result of the poll shall be deemed to be the resolution
            of the meeting at which the poll is demanded.
        \end{enumerate}
        \item \begin{enumerate}[label=(\alph*)]
            \item A poll demanded on the election of a person to chair
            a meeting or on a question of adjournment must be
            taken immediately.
            \item A poll demanded on any other question must be taken
            either immediately or at such time and place as the
            person who is chairing the meeting directs.
            \item The poll must be taken within thirty days after it has
            been demanded.
            \item A poll demanded on any other question must be taken
            either immediately or at such time and place as the
            person who is chairing the meeting directs.
            \item The poll must be taken within thirty days after it has
            been demanded.
            \item If the poll is not taken immediately at least seven clear
            days' notice shall be given specifying the time and place
            at which the poll is to be taken.
            \item If a poll is demanded the meeting may continue to
            deal with any other business that may be conducted at
            the meeting.
        \end{enumerate}
    \end{enumerate}
    
    \section{Content of proxy notices}
    \item \begin{enumerate}[label=(\arabic*)]
        \item Proxies may only validly be appointed by a notice in writing (a
        `proxy notice') which -
        \begin{enumerate}[label=(\alph*)]
            \item states the name and address of the member appointing
            the proxy;
            \item identifies the person appointed to be that member's
            proxy and the general meeting in relation to which that
            person is appointed;
            \item is signed by or on behalf of the member appointing the
            proxy, or is authenticated in such manner as the directors
            may determine; and
            \item is delivered to the charity in accordance with the articles
            and any instructions contained in the notice of the general
            meeting to which they relate.
        \end{enumerate}
        \item The charity may require proxy notices to be delivered in
        a particular form, and may specify different forms for
        different purposes.
        \item Proxy notices may specify how the proxy appointed under them
        is to vote (or that the proxy is to abstain from voting) on one or
        more resolutions.
        \item Unless a proxy notice indicates otherwise, it must be treated as -
        \begin{enumerate}[label=(\alph*)]
            \item allowing the person appointed under it as a proxy
            discretion as to how to vote on any ancillary or procedural
            resolutions put to the meeting; and
            \item appointing that person as a proxy in relation to any
            adjournment of the general meeting to which it relates as
            well as the meeting itself.
        \end{enumerate}
    \end{enumerate}
\end{enumerate}
\begin{enumerate}[label=\arabic*A, start=22]
    \section{Delivery of proxy notices}
    \item \begin{enumerate}[label=(\arabic*)]
        \item A person who is entitled to attend, speak or vote (either on a
        show of hands or on a poll) at a general meeting remains so
        entitled in respect of that meeting or any adjournment of it,
        even though a valid proxy notice has been delivered to the
        charity by or on behalf of that person
        \item An appointment under a proxy notice may be revoked by
        delivering to the charity a notice in writing given by or on behalf
        of the person by whom or on whose behalf the proxy notice
        was given.
        \item A notice revoking a proxy appointment only takes effect if it is
        delivered before the start of the meeting or adjourned meeting
        to which it relates.
        \item If a proxy notice is not executed by the person appointing the
        proxy, it must be accompanied by written evidence of the
        authority of the person who executed it to execute it on the
        appointor's behalf.
    \end{enumerate}
\end{enumerate}
\begin{enumerate}[label=\arabic*, start=23]
    \section{Written resolutions}
    \item \begin{enumerate}[label=(\arabic*)]
        \item A resolution in writing agreed by a simple majority (or in the
        case of a special resolution by a majority of not less than 75\%)
        of the members who would have been entitled to vote upon it
        had it been proposed at a general meeting shall be effective
        provided that:
        \begin{enumerate}[label=(\alph*)]
            \item a copy of the proposed resolution has been sent to every
            eligible member;
            \item a simple majority (or in the case of a special resolution a
            majority of not less than 75\%) of members has signified
            its agreement to the resolution; and
            \item it is contained in an authenticated document which has
            been received at the registered office within the period of
            28 days beginning with the circulation date.
        \end{enumerate}
        \item A resolution in writing may comprise several copies to which
        one or more members have signified their agreement.
    \end{enumerate}
    
    \section{Votes of members}
    \item  Subject to article 11, every member, whether an individual or an
    organisation, shall have one vote.
    \item  Any objection to the qualification of any voter must be raised at the
    meeting at which the vote is tendered and the decision of the person
    who is chairing the meeting shall be final.
    \item \begin{enumerate}[label=(\arabic*)]
        \item Any organisation that is a member of the charity may
        nominate any person to act as its representative at any meeting
        of the charity.
        \item  The organisation must give written notice to the charity of the
        name of its representative. The representative shall not be
        entitled to represent the organisation at any meeting unless the
        notice has been received by the charity. The representative may
        continue to represent the organisation until written notice to the
        contrary is received by the charity.
        \item  Any notice given to the charity will be conclusive evidence that
        the representative is entitled to represent the organisation or
        that his or her authority has been revoked. The charity shall not
        be required to consider whether the representative has been
        properly appointed by the organisation.
    \end{enumerate}
    
    \section{Directors}
    \item \begin{enumerate}[label=(\arabic*)]
        \item A director must be a natural person aged 16 years or older.
        \item No one may be appointed a director if he or she would be
        disqualified from acting under the provisions of article 39.
    \end{enumerate}
    \item The minimum number of directors shall be [ ] but (unless
    otherwise determined by ordinary resolution) shall not be subject
    to any maximum.
    \item The first directors shall be those persons notified to Companies House as
    the first directors of the charity.
    \item A director may not appoint an alternate director or anyone to act on his
    or her behalf at meetings of the directors.
    
    \section{Powers of directors}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors shall manage the business of the charity and may
        exercise all the powers of the charity unless they are subject to
        any restrictions imposed by the Companies Acts, the articles or
        any special resolution.
        \item No alteration of the articles or any special resolution shall have
        retrospective effect to invalidate any prior act of the directors.
        \item Any meeting of directors at which a quorum is present at the
        time the relevant decision is made may exercise all the powers
        exercisable by the directors.
    \end{enumerate}
    
    \section{Retirement of directors}
    \item At the first annual general meeting all the directors must retire from
    office unless by the close of the meeting the members have failed to
    elect sufficient directors to hold a quorate meeting of the directors. At
    each subsequent annual general meeting one-third of the directors or, if
    their number is not three or a multiple of three, the number nearest to
    one-third, must retire from office. If there is only one director he or she
    must retire.
    \item \begin{enumerate}[label=(\arabic*)]
    \item The directors to retire by rotation shall be those who have been
    longest in office since their last appointment. If any directors
    became or were appointed directors on the same day those to
    retire shall (unless they otherwise agree among themselves) be
    determined by lot.
    \item If a director is required to retire at an annual general meeting by
    a provision of the articles the retirement shall take effect upon
    the conclusion of the meeting.
    \end{enumerate}
    
    \section{Appointment of directors}
    \item  The charity may by ordinary resolution:
    \begin{enumerate}[label=(\arabic*)]
    \item  appoint a person who is willing to act to be a director; and
    \item  determine the rotation in which any additional directors are
    to retire.
    \end{enumerate}
    \item No person other than a director retiring by rotation may be appointed a
    director at any general meeting unless:
    \begin{enumerate}[label=(\arabic*)]
        \item he or she is recommended for re-election by the directors; or
        \item not less than fourteen nor more than thirty-five clear days
        before the date of the meeting, the charity is given a
        notice that:
        \begin{enumerate}[label=(\alph*)]
            \item is signed by a member entitled to vote at the meeting;
            \item states the member's intention to propose the
            appointment of a person as a director;
            \item contains the details that, if the person were to be
            appointed, the charity would have to file at Companies
            House; and
            \item is signed by the person who is to be proposed to show his
            or her willingness to be appointed.
        \end{enumerate}
    \end{enumerate}
    \item All members who are entitled to receive notice of a general meeting
    must be given not less than seven nor more than twenty-eight clear
    days' notice of any resolution to be put to the meeting to appoint a
    director other than a director who is to retire by rotation.
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors may appoint a person who is willing to act to be
        a director.
       \item A director appointed by a resolution of the other directors must
        retire at the next annual general meeting and must not be
        taken into account in determining the directors who are to retire
        by rotation.
    \end{enumerate}
    \item The appointment of a director, whether by the charity in general
    meeting or by the other directors, must not cause the number of
    directors to exceed any number fixed as the maximum number
    of directors
    
    \section{Disqualification and removal of directors}
    \item A director shall cease to hold office if he or she:
    \begin{enumerate}[label=(\arabic*)]
        \item ceases to be a director by virtue of any provision in the
        Companies Acts or is prohibited by law from being a director;
        \item is disqualified from acting as a trustee by virtue of sections
        178 and 179 of the Charities Act 2011 (or any statutory
        re-enactment or modification of those provisions);
        \item ceases to be a member of the charity;
        \item in the written opinion, given to the company, of a registered
        medical practitioner treating that person, has become physically
        or mentally incapable of acting as a director and may remain so
        for more than three months;
        \item resigns as a director by notice to the charity (but only if at
        least two directors will remain in office when the notice of
        resignation is to take effect); or
        \item is absent without the permission of the directors from all their
        meetings held within a period of six consecutive months and
        the directors resolve that his or her office be vacated.
    \end{enumerate}
    
    \section{Remuneration of directors}
    \item The directors must not be paid any remuneration unless it is authorised
    by article 7.
    
    \section{Proceedings of directors}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors may regulate their proceedings as they think fit,
        subject to the provisions of the articles.
        \item Any director may call a meeting of the directors.
        \item The secretary (if any) must call a meeting of the directors if
        requested to do so by a director.
        \item Questions arising at a meeting shall be decided by a majority
        of votes.
        \item In the case of an equality of votes, the person who is chairing
        the meeting shall have a second or casting vote.
        \item A meeting may be held by suitable electronic means agreed by
        the directors in which each participant may communicate with
        all the other participants.
    \end{enumerate}
    
    \item \begin{enumerate}[label=(\arabic*)]
            \item No decision may be made by a meeting of the directors unless
            a quorum is present at the time the decision is purported to be
            made. [`Present' includes being present by suitable electronic
            means agreed by the directors in which a participant or
            participants may communicate with all the other participants.]
            \item The quorum shall be two or the number nearest to one-third
            of the total number of directors, whichever is the greater, or
            such larger number as may be decided from time to time by
            the directors.
            \item A director shall not be counted in the quorum present when any
            decision is made about a matter upon which that director is not
            entitled to vote.
    \end{enumerate}
    \item If the number of directors is less than the number fixed as the quorum,
    the continuing directors or director may act only for the purpose of
    filling vacancies or of calling a general meeting.
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors shall appoint a director to chair their meetings and
        may at any time revoke such appointment.
        \item If no-one has been appointed to chair meetings of the directors
        or if the person appointed is unwilling to preside or is not
        present within ten minutes after the time appointed for the
        meeting, the directors present may appoint one of their number
        to chair that meeting.
        \item The person appointed to chair meetings of the directors shall
        have no functions or powers except those conferred by the
        articles or delegated to him or her by the directors.
    \end{enumerate}
    \item \begin{enumerate}[label=(\arabic*)]
        \item A resolution in writing or in electronic form agreed by all of the
        directors entitled to receive notice of a meeting of the directors
        and to vote upon the resolution shall be as valid and effectual as
        if it had been passed at a meeting of the directors duly convened
        and held.
        \item The resolution in writing may comprise several documents
        containing the text of the resolution in like form to each of
        which one or more directors has signified their agreement.
    \end{enumerate}
    
    \section{Delegation}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors may delegate any of their powers or functions
        to a committee of two or more directors but the terms of any
        delegation must be recorded in the minute book.
        \item The directors may impose conditions when delegating, including
        the conditions that:
        \begin{enumerate}[label=(\alph*)]
            \item the relevant powers are to be exercised exclusively by the
            committee to whom they delegate;
            \item no expenditure may be incurred on behalf of the charity
            except in accordance with a budget previously agreed
            with the directors.
        \end{enumerate}
        \item The directors may revoke or alter a delegation.
        \item All acts and proceedings of any committees must be fully and
        promptly reported to the directors.
    \end{enumerate}
    
    \section{Validity of directors' decisions}
    \item \begin{enumerate}[label=(\arabic*)]
        \item Subject to article 47(2), all acts done by a meeting of directors,
        or of a committee of directors, shall be valid notwithstanding
        the participation in any vote of a director:
        \begin{enumerate}[label=(\alph*)]
        \item who was disqualified from holding office;
        \item who had previously retired or who had been obliged by
        the constitution to vacate office;
        \item who was not entitled to vote on the matter, whether by
        reason of a conflict of interests or otherwise;
        if without:
        \item the vote of that director; and
        \item that director being counted in the quorum;
        the decision has been made by a majority of the directors at a
        quorate meeting.
        \end{enumerate}
        \item Article 47(1) does not permit a director or a connected person
        to keep any benefit that may be conferred upon him or her by a
        resolution of the directors or of a committee of directors if, but
        for article 47(1), the resolution would have been void, or if the
        director has not complied with article 8.
    \end{enumerate}
    
    \section{Seal}
    \item If the charity has a seal it must only be used by the authority of the
    directors or of a committee of directors authorised by the directors. The
    directors may determine who shall sign any instrument to which the
    seal is affixed and unless otherwise so determined it shall be signed by
    a director and by the secretary (if any) or by a second director.
    
    \section{Minutes}
    \item The directors must keep minutes of all:
    \begin{enumerate}[label=(\arabic*)]
        \item appointments of officers made by the directors;
        \item proceedings at meetings of the charity;
        \item meetings of the directors and committees of directors including:
        \begin{enumerate}[label=(\alph*)]
            \item the names of the directors present at the meeting;
            \item the decisions made at the meetings; and
            \item where appropriate the reasons for the decisions.
        \end{enumerate}
    \end{enumerate}
    
    \section{Accounts}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors must prepare for each financial year accounts as
        required by the Companies Acts. The accounts must be prepared
        to show a true and fair view and follow accounting standards
        issued or adopted by the Accounting Standards Board or its
        successors and adhere to the recommendations of applicable
        Statements of Recommended Practice.
        \item The directors must keep accounting records as required by the
        Companies Act.
    \end{enumerate}
    
    \section{Annual Report and Return and Register of Charities}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors must comply with the requirements of the
        Charities Act 2011 with regard to the:
        \begin{enumerate}[label=(\alph*)]
            \item transmission of a copy of the statements of account to
            the Commission;
            \item preparation of an Annual Report and the transmission of a
            copy of it to the Commission;
            \item preparation of an Annual Return and its transmission to
            the Commission.
        \end{enumerate}
        \item The directors must notify the Commission promptly of
        any changes to the charity's entry on the Central Register
        of Charities.
    \end{enumerate}
    
    \section{Means of communication to be used}
    \item \begin{enumerate}[label=(\arabic*)]
        \item Subject to the articles, anything sent or supplied by or to the
        charity under the articles may be sent or supplied in any way
        in which the Companies Act 2006 provides for documents or
        information which are authorised or required by any provision of
        that Act to be sent or supplied by or to the charity.
        \item Subject to the articles, any notice or document to be sent or
        supplied to a director in connection with the taking of decisions
        by directors may also be sent or supplied by the means by
        which that director has asked to be sent or supplied with such
        notices or documents for the time being.
    \end{enumerate}
    \item Any notice to be given to or by any person pursuant to the articles:
    \begin{enumerate}[label=(\arabic*)]
        \item must be in writing; or
        \item must be given in electronic form.
    \end{enumerate}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The charity may give any notice to a member either:
        \begin{enumerate}[label=(\alph*)]
            \item personally; or
            \item by sending it by post in a prepaid envelope addressed to
            the member at his or her address; or
            \item by leaving it at the address of the member; or
            \item by giving it in electronic form to the member's address.
            \item by placing the notice on a website and providing the
            person with a notification in writing or in electronic
            form of the presence of the notice on the website. The
            notification must state that it concerns a notice of a
            company meeting and must specify the place date and
            time of the meeting.
        \end{enumerate}
        \item A member who does not register an address with the charity
        or who registers only a postal address that is not within the
        United Kingdom shall not be entitled to receive any notice from
        the charity.
    \end{enumerate}
    \item A member present in person at any meeting of the charity shall be
    deemed to have received notice of the meeting and of the purposes for
    which it was called.
    \item \begin{enumerate}[label=(\arabic*)]
        \item Proof that an envelope containing a notice was properly
        addressed, prepaid and posted shall be conclusive evidence that
        the notice was given.
        \item Proof that an electronic form of notice was given shall be
        conclusive where the company can demonstrate that it was
        properly addressed and sent, in accordance with section 1147 of
        the Companies Act 2006.
        \item In accordance with section 1147 of the Companies Act 2006
        notice shall be deemed to be given:
        \begin{enumerate}[label=(\alph*)]
            \item 48 hours after the envelope containing it was posted; or
            \item in the case of an electronic form of communication, 48
            hours after it was sent.
        \end{enumerate}
    \end{enumerate}
    
    \section{Indemnity}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The charity shall indemnify a relevant director against any
        liability incurred in that capacity, to the extent permitted by
        sections 232 to 234 of the Companies Act 2006
        \item In this article a `relevant director' means any director or former
        director of the charity.
    \end{enumerate}
    
    \section{Rules}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The directors may from time to time make such reasonable and
        proper rules or bye laws as they may deem necessary
        or expedient for the proper conduct and management of
        the charity.
        \item The bye laws may regulate the following matters but are not
        restricted to them:
        \begin{enumerate}[label=(\alph*)]
            \item the admission of members of the charity (including the
            admission of organisations to membership) and the
            rights and privileges of such members, and the entrance
            fees, subscriptions and other fees or payments to be
            made by members;
            \item the conduct of members of the charity in relation to one
            another, and to the charity's employees and volunteers;
            \item the setting aside of the whole or any part or parts of the
            charity's premises at any particular time or times or for
            any particular purpose or purposes;
            \item the procedure at general meetings and meetings of the
            directors in so far as such procedure is not regulated by
            the Companies Acts or by the articles;
            \item generally, all such matters as are commonly the subject
            matter of company rules.
        \end{enumerate}
        \item The charity in general meeting has the power to alter, add to or
        repeal the rules or bye laws.
        \item The directors must adopt such means as they think sufficient
        to bring the rules and bye laws to the notice of members of
        the charity.
        \item The rules or bye laws shall be binding on all members of the
        charity. No rule or bye law shall be inconsistent with, or shall
        affect or repeal anything contained in, the articles.
    \end{enumerate}
    
    \section{Disputes}
    \item If a dispute arises between members of the charity about the validity
    or propriety of anything done by the members of the charity under
    these articles, and the dispute cannot be resolved by agreement, the
    parties to the dispute must first try in good faith to settle the dispute by
    mediation before resorting to litigation.
    
    \section{Dissolution}
    \item \begin{enumerate}[label=(\arabic*)]
        \item The members of the charity may at any time before, and in
        expectation of, its dissolution resolve that any net assets of
        the charity after all its debts and liabilities have been paid,
        or provision has been made for them, shall on or before the
        dissolution of the charity be applied or transferred in any of the
        following ways:
        \begin{enumerate}[label=(\alph*)]
            \item directly for the Objects; or
            \item by transfer to any charity or charities for purposes similar
            to the Objects; or
            \item to any charity or charities for use for particular purposes
            that fall within the Objects.
        \end{enumerate}
        \item Subject to any such resolution of the members of the charity,
        the directors of the charity may at any time before and in
        expectation of its dissolution resolve that any net assets of
        the charity after all its debts and liabilities have been paid, or
        provision made for them, shall on or before dissolution of the
        charity be applied or transferred:
        \begin{enumerate}[label=(\alph*)]
            \item directly for the Objects; or
            \item by transfer to any charity or charities for purposes similar
            to the Objects; or
            \item to any charity or charities for use for particular purposes
            that fall within the Objects.
        \end{enumerate}
        \item In no circumstances shall the net assets of the charity be paid
        to or distributed among the members of the charity (except
        to a member that is itself a charity) and if no resolution in
        accordance with article 60(1) is passed by the members or
        the directors the net assets of the charity shall be applied for
        charitable purposes as directed by the Court or the Commission.
    \end{enumerate}
    
    \section{Interpretation}
    \item In article 7, sub-clause (2) of article 9 and sub-clause (2) of article 47
    `connected person' means:
    \begin{enumerate}[label=(\arabic*)]
        \item a child, parent, grandchild, grandparent, brother or sister of
        the director;
        \item the spouse or civil partner of the director or of any person
        falling within sub-clause (1) above;
        \item a person carrying on business in partnership with the director or
        with any person falling within sub-clause (1) or (2) above;
        \item an institution which is controlled –
        \begin{enumerate}[label=(\alph*)]
            \item by the director or any connected person falling within
            sub-clause (1), (2), or (3) above; or
            \item by two or more persons falling within sub-clause 4(a),
            when taken together
        \end{enumerate}
        \item a body corporate in which –
        \begin{enumerate}[label=(\alph*)]
            \item the director or any connected person falling within subclauses (1) to (3) has a substantial interest; or
            \item two or more persons falling within sub-clause (5)(a) who,
            when taken together, have a substantial interest.
            \item Sections 350 – 352 of the Charities Act 2011 apply for the
            purposes of interpreting the terms used in this article.
        \end{enumerate}
    \end{enumerate}
\end{enumerate}

\end{document}
